\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}
\usepackage[margin=1.4cm]{geometry}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.15in}
 \addtolength{\textwidth}{0.3in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{0pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}\vspace{0pt}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}



\begin{document}
%----------HEADING----------
\begin{center}
    {\Large \scshape Mia Truong} \\[-1pt]
    \footnotesize
    \faPhone~\underline{(509) 994-7104} ~
    \faEnvelope~\underline{trangmtruong@icloud.com} ~
    \faLinkedin~\href{https://www.linkedin.com/in/trangmtruong}{\underline{linkedin.com/in/trangmtruong}} ~
    \faGithub~\href{https://github.com/trangmtruong}{\underline{github.com/trangmtruong}} ~
    \faBriefcase~\href{https://www.miatruong.com/}{\underline{miatruong.com}}
\end{center}
\vspace{-6pt}


%-----------Summary-----------
\section{Professional Summary}
    \vspace{2pt}
\small
\noindent \textbf{Full-Stack Developer} with a \textbf{people-first} approach, known for strong \textbf{collaboration}, \textbf{adaptability}, and \textbf{communication}.\\
    \vspace{2pt}
\noindent Combines design intuition with practical \textbf{problem-solving} to deliver thoughtful, \textbf{user-focused solutions}.\\
\noindent Recognized for \textbf{positivity}, \textbf{reliability}, and a calm, \textbf{detail-driven} mindset that elevates every team.
\normalsize

 \vspace{-2pt}
  %-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
    \vspace{-2pt}
\small
\textbf{Languages \& Tools:} JavaScript, TypeScript, HTML, CSS, SQL, Git, GitHub, Postman, Figma \\
    \vspace{2pt}
\textbf{Frameworks:} React, Next.js, Node.js, Express, Tailwind, Vite, Storybook, Headless UI \\
    \vspace{2pt}
\textbf{Databases:} MongoDB, MySQL, KeystoneJS, DBeaver \\
    \vspace{2pt}
\textbf{Other:} AWS (S3, CloudFront, EC2, Route 53), NGINX, PM2, OAuth 2.0, Jest, Agile
\normalsize


%-----------Experience---------------
\section{Work Experience}
\resumeSubHeadingListStart

\resumeSubheading
 {PROJXON — Web Developer Intern}{Jun 2025 -- Present}
  {momentuminternshipprogram.com}{Remote}
\resumeItemListStart
  \resumeItem{Built the Momentum Internship Program site using React, TypeScript, TailwindCSS.}
  \resumeItem{Integrated Nodemailer + OAuth2 for email automation; tested endpoints in Postman.}
  \resumeItem{Deployed via AWS (S3, CloudFront, EC2, Route53) with PM2 + Nginx and SSL.}
  \resumeItem{Collaborated cross-functionally in weekly agile stand-ups and sprint reviews.}
\resumeItemListEnd



\resumeSubheading
  {DROPS Externship — Software Engineer Extern}{Apr 2025 -- Jun 2025}
  {TripleTen}{Remote}
  \vspace{-2pt}
\resumeItemListStart
  \resumeItem{Built reusable UI components with React, TypeScript, Tailwind, and GraphQL.}
  \resumeItem{Integrated frontend with Keystone + MySQL backend using GraphQL Codegen.}
  \resumeItem{Collaborated in an agile team, participating in sprints, code reviews, and daily standups.}
\resumeItemListEnd


\resumeSubheading
  {WTWR (What To Wear) — Software Engineer Student}{Apr 2024 -- Nov 2024}
  {TripleTen}{Remote}
  \vspace{-2pt}
\resumeItemListStart
  \resumeItem{Created responsive React + Vite app with user auth and weather-based outfit logic.}
  \resumeItem{Developed Node.js + Express API with MongoDB and Jest unit tests; deployed on GCP.}
  \resumeItem{Implemented dynamic weather API filtering and improved UI performance by 20\%.}
\resumeItemListEnd



\resumeSubheading
  {TripleTen Code Jams — Software Engineer Participant}{Jul 2024 \& Jan 2025}
  {TripleTen}{Remote}
  \vspace{-2pt}
\resumeItemListStart
  \resumeItem{Won 1st place twice for front-end projects using HTML, CSS, and JavaScript.}
  \resumeItem{Delivered light/dark modes, animations, and branding assets under deadlines.}
  \resumeItem{Strengthened teamwork, time management, and creative problem-solving under pressure.}
\resumeItemListEnd


\resumeSubHeadingListEnd
    

%-----------PROJECTS-----------
\section{Projects} 
    \vspace{-2pt}
    
\resumeSubHeadingListStart

\resumeProjectHeading
{\textbf{Momentum Internship Program Website} $|$ \emph{\href{https://github.com/trangmtruong/MIP-site}{Source Code}}}{React | TypeScript | Tailwind | AWS}
\resumeItemListStart
  \resumeItem{Built and deployed full-stack platform supporting intern recruitment and blog CMS.}
  \resumeItem{Configured AWS CloudFront + S3 hosting, Route 53 domain, and automated deployments.}
\resumeItemListEnd

    \vspace{-8pt}

\resumeProjectHeading
{\textbf{WTWR – Wardrobe App} $|$ \emph{\href{https://github.com/trangmtruong/se_project_react}{Source Code}}}{React | Node.js | MongoDB}
\resumeItemListStart
  \resumeItem{Weather-based outfit recommender integrating OpenWeather API and secure user auth.}
  \resumeItem{Implemented Node.js backend with CRUD and centralized error handling middleware.}
\resumeItemListEnd

\resumeSubHeadingListEnd
    \vspace{-8pt}


\resumeSubHeadingListEnd

 %-----------EDUCATION-----------
\section{Education}

\resumeSubHeadingListStart
\resumeSubheading
  {TripleTen Software Engineering Bootcamp}{Graduated: Jan 2025}
  {Certificate in Full-Stack Software Engineering}{Remote}
\resumeSubheading
  {Eastern Washington University}{Graduated: 2015}
  {Pre-Pharmacy Studies}{Cheney, WA}
\resumeSubHeadingListEnd
    \vspace{-6pt}

\end{document}